\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

Various constraint languages exist or are being developed that support more or less of these constraint types. For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}. Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

@@

\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions. ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs. \emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources. Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

>>>>

Various constraint languages exist or are being developed that support more or less of these constraint types. For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}. Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

@@

\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions. ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs. \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources. Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.
